---
title: "Project 1: Network Formation"
Authors: "Tianyuan Wang, Haonan Yang, Yuehan Yang, Yuanwen Yue"
output: html_notebook
---

In this file, we do the first step of our project: network formation.

```{r, message=F}
library(rtweet)
library(dplyr)
library(igraph)
library(ggraph)
library(graphlayouts)
```

There are 240 members in our lists, containing celebrities and organizations who care about environmental issues. The celebrities and organization are from different fields, such as politicains, entrepreneurs, scholars, artists, activists, etc. The celebrities and organizations in our list are from the following lists:

(1) ClimateWeekNYC: 2020 Top 100 Twitter accounts about climate action (https://www.climateweeknyc.org/climate-groups-top-100-twitter-accounts-2020)

(2) Onalytica: Environmental Sustainability (2019) Top 100 Twitter influencers 
( https://onalytica.com/blog/posts/environmental-sustainability-top-100-influencers/)

(3) Corporate Knights: Top 100 Eco-influencers on Twitter (2015) (https://www.corporateknights.com/channels/connected-planet/top-100-eco-influencers-twitter-14295615/)

```{r}
env_celebritiesdf <- lists_members(list_id = 1371127388474462208)
head(users)
nrow(users)
```

```{r}
save(env_celebritiesdf,file="env_celebritiesdf.RData")
```

We found that there's nearly no retweet between our selected celebrities, so friend network is a better option to analyze the connections among the selected celebrities.
```{r}
friends <- get_friends(user=env_celebritiesdf$user_id)
save(friends,file="friends.RData")
```

In this step, we select every celebrity's Twitter friends who are also the celebrities we selected.
```{r}
load("env_celebritiesdf.RData")
load("friends.RData")
friends %>% filter(user_id %in% env_celebritiesdf$user_id) -> friendsdf
```

Celebrities as vertices and their friendship (they're twitter friends or not) as edges.
```{r}
env_celebritiesdf %>% select (id=user_id,name=screen_name)->vertices
friendsdf %>% select(from=user, to=user_id) %>% group_by(from,to) -> edges
```

Firstly we make our graph as directed. Later, when we make communities and k-core, we change it to "undirected".
```{r}
graph <- tbl_graph(nodes=vertices, edges = edges, node_key = "id", directed = TRUE)
graph
```

Draw the first graph. We found that there are mant nodes outside without any link.
```{r}
graph %>% ggraph(layout="fr") +  geom_edge_link0(color="gray", arrow=arrow(type = "closed", length = unit(2,"pt")))  + geom_node_point( shape=19, color="lightblue") + theme_graph()
```

Have a look of the degree distribution.
```{r}
graph %>% 
  activate(vertices) %>% 
  mutate(deg = centrality_degree()) %>%pull(deg)->degree
hist(degree,xlim=range(0,max(degree)+20),breaks=120)

```

Screen out nodes haing at least one link. We will only analyze the connected component.
```{r}
env_celebritiesdf %>% filter((user_id %in% friendsdf$user) | (user_id %in% friendsdf$user_id) )->coredf

coredf %>% select (id=user_id,name=screen_name)-> core_vertices

```

Now we make the graph undirected. Later we will analyze its communities and k-core.
```{r}
core_graph <- tbl_graph(nodes=core_vertices, edges = edges, node_key = "id", directed = FALSE)
```

Draw the graph of the connected component.
```{r}
core_graph %>% ggraph(layout="stress") +  geom_edge_link0(color="gray", arrow=arrow(type = "closed", length = unit(2,"pt")))  + geom_node_point( shape=19, color="lightblue") + theme_graph()
```

Degree distribution of the connected component.
```{r}
core_graph %>% 
  activate(vertices) %>% 
  mutate(deg = centrality_degree()) %>%pull(deg)->core_degree
hist(core_degree,xlim=c(0,100),breaks=100,main = "Degree Distribution")
```
Analyzing communities using louvain method.
```{r}
core_graph %>% activate(vertices) %>%
  mutate(deg = centrality_degree()) %>%
  mutate(community = as.character(group_louvain())) -> com_graph
```

Draw the communities graph.
```{r}
com_graph %>%
  ggraph("stress") + geom_edge_link(edge_color="gray66",edge_width=0.3) + geom_node_point(aes(color=community,size=deg)) + 
   geom_node_text(aes(filter = deg>=26, label = name))+
  theme_graph()
```

Calculate the modularity of the communities.
```{r}
com_graph %>% 
  mutate(modularity = graph_modularity(community)) %>% 
  pull(modularity) %>% 
  head(1)
```
Because the modularity above shows there is not obvious community formation, we next analyze the hierarchical structure of the graph, in other words, k-core.
```{r}
com_graph %>% 
  activate(vertices) %>% 
  mutate(kcore=as.character(node_coreness())) ->com_graph 
  
ggraph(com_graph,"stress") +
  geom_edge_link0(edge_colour = "grey66")+
  geom_node_point(aes(fill = kcore,size = deg),shape = 21)+
  scale_edge_width_continuous(range = c(0.2,1.2))+
  scale_size_continuous(range = c(1,5))+
  coord_fixed()+
  theme_graph()+
  theme()
```
It took some time to search the internet and divide the celebrities into different fields. When fields division is done, we upload the fields information and merge it to our previous data frame.
```{r}
com_graph %>%activate(nodes)%>%as_tibble()->comdf
```

```{r}
fields<-read.csv("celebrity.csv")
fields %>% select(name=screen_name,field)->fields
```

```{r}
fieldsdf<-inner_join(comdf,fields,by="name")
#head(fieldsdf)
```

```{r}
#save(fieldsdf,file="fields.RData")
write.csv(fieldsdf,file="fields.csv")
```

```{r}
head(fieldsdf)
```

Calculate the assortativity of field. The result shows celebrities in the same fields don't tend to merge into the same cluster.
```{r}
fields_graph <- tbl_graph(nodes=fieldsdf, edges = edges, node_key = "id", directed = FALSE)
fields_graph %>% 
  mutate(assort=graph_assortativity(field)) %>% 
  pull(assort)  %>% 
  head(1)
```
Draw the graph colored with fields.
```{r}
fields_graph %>%
  ggraph("stress") + geom_edge_link0(edge_color="gray66",edge_width=0.1) + geom_node_point(aes(color=field,size=deg)) + 
   #geom_node_text(aes(filter = deg>=26, label = name))+
  theme_graph(base_family = 'Helvetica')
```
Export the three graphs created above. The iamge quality in the form of "pdf" is better than "png" or "jpge". However, there is always an error about the font and we cannot export the legends. We just export the pure graph here and then add the legend with the help of other softwares.
```{r}
# Open a pdf file
pdf("fields.pdf") 
# 2. Create a plot
ggraph(fields_graph,"stress") + geom_edge_link(edge_color="gray66",edge_width=0.15) + geom_node_point(aes(color=field,size=deg)) + 
  coord_fixed()+
  theme_graph(base_family = 'Helvetica')
# Close the pdf file
dev.off() 
```

```{r}
pdf("communities.pdf")
ggraph(com_graph,"stress") + geom_edge_link(edge_color="gray66",edge_width=0.15) +     geom_node_point(aes(color=community,size=deg)) + 
  coord_fixed()+
  theme_graph(base_family = 'Helvetica')
dev.off()
```
```{r}
pdf("kcore.pdf") 

ggraph(com_graph,"stress") +
  geom_edge_link0(edge_colour = "grey66",edge_width=0.15)+
  geom_node_point(aes(fill = kcore,size = deg),shape = 21)+
  coord_fixed()+
  theme_graph(base_family = 'Helvetica')+
  theme()

dev.off() 
```
Assign every field an id to make the boxplot looks better.
```{r}
fieldsdf$fields_id[fieldsdf$field=="scientist"]=1
fieldsdf$fields_id[fieldsdf$field=="environmentalist"]=2
fieldsdf$fields_id[fieldsdf$field=="NGO officer"]=3
fieldsdf$fields_id[fieldsdf$field=="organisation"]=4

fieldsdf$fields_id[fieldsdf$field=="writer and journalist"]=5
fieldsdf$fields_id[fieldsdf$field=="actor, singer and host"]=6
fieldsdf$fields_id[fieldsdf$field=="politician"]=7
fieldsdf$fields_id[fieldsdf$field=="social activist"]=8
fieldsdf$fields_id[fieldsdf$field=="businessman"]=9
fieldsdf$fields_id[fieldsdf$field=="athelete"]=10
head(fieldsdf)
```

Export box plot of the fields and degree distribution.
```{r}
pdf("fields_degrees.pdf") 

ggplot(fieldsdf,aes(x=field, y=deg, fill=field)) + 
     geom_boxplot() +
     xlab("Fields") +
     ylab('Degrees')+theme(axis.text.x=element_blank(),text = element_text(size=22),panel.grid.major=element_line(colour=NA),panel.grid.minor=element_line(colour=NA))

dev.off() 
```



Export a stacked bar plot of communities and fields.
```{r}
pdf("fields_community.pdf")

ggplot(fieldsdf,aes(x=community, y=fields_id, fill=field)) + 
     geom_bar(stat = "identity") +
     xlab("Community") +
     ylab('Fields')+theme(text = element_text(size=20))+theme_test()

dev.off() 
```

Draw box plot of degree and k-core.
```{r}
pdf("degreee_k-core.pdf")
boxplot(as.numeric(fieldsdf$kcore)~fieldsdf$deg,
        xlab="degrees",
ylab="k-core",)
dev.off()
```



